\LARGE \bf Human-Robot Interaction: Tackling the AI Challenges

### 2014-05-05 paper.tex
Major rewrite of the SPARK section
Based on my PhD work

\subsection{Situation Assessment, Human Awareness, Perspective Taking}
\label{sect|sit-ass}

@@

{\sc Spark} is designed to run and continously update the knowledge base (in our
experiments, it runs at about 10Hz). At each steps, it re-computes spatial
relationships and affordances for the whole scene, and send the delta (new
relations and relations that do not hold anymore) to the knowledge base. This
approach may raise scalability concerns (we did not however hit such issues in
our constrainted scenarios), but greatly simplifies the management of the
\emph{dynamics} of the knowledge (\emph{When do I discard outdated knowledge?
When do I update it?}). Since it is equivalent to a reset of the reasoner
domain, it also hides issues linked to non-monotonic reasoning
(see~\cite{McCarthy2007} for a discussion on that question).

\begin{figure*}[ht!]
   \begin{center}
%
       \subfigure[Initial state]{%
%           \label{fig:wuweiPhoto}
           \includegraphics[width=0.5\textwidth]{etat2-P1010769_brightened-v2.jpg}
       }%
       \subfigure[Corresponding 3D model view]{%
%          \label{fig:sparkScreenshot}
          \includegraphics[width=0.43\textwidth]{etat2_photo.png}
       }\\ %  ------- End of the first row ----------------------%
%
   \end{center}

   \caption{The toy scenario pictured here involves videotapes that have to be
       manipulated, with other objects used as supports and containers.  After
       identification and localisation of the set of objects and acquisition of
       the position and posture of the human partner, the robot is able to
       compute that two tapes only are reachable by itself: the
       \concept{LOTR\_TAPE} (black in the 3D model) and \concept{GREY\_TAPE}.
       The third tape \concept{WALLE\_TAPE} (white in the 3D model) and the
   trashbin \concept{PINK\_TRASHBIN} are only reachable by the human. The
   corresponding symbolic facts are listed in Table~\ref{table|beliefsfig7}.  }%

@@

\begin{table}
\begin{center}
    \subfigure{
\begin{tabular}{l}
\hline
Robot's beliefs about itself (\emph{robot's model})\\
\hline
  \hspace{0.7cm}\stmt{PINK\_TRASHBIN isReachable false}\\
  \hspace{0.7cm}\stmt{WALLE\_TAPE isReachable {\bf false}}\\
  \hspace{0.7cm}\stmt{LOTR\_TAPE isReachable {\bf true}}\\
  \hspace{0.7cm}\stmt{GREY\_TAPE isReachable {\bf true}}\\
  \hspace{0.7cm}\stmt{WALLE\_TAPE isVisible true}\\
  \hspace{0.7cm}\stmt{LOTR\_TAPE isVisible true}\\
  \hspace{0.7cm}\stmt{GREY\_TAPE isVisible true}\\
  \hspace{0.7cm}\stmt{WALLE\_TAPE isOn TABLE}\\
  \hspace{0.7cm}\stmt{LOTR\_TAPE isOn TABLE}\\
  \hspace{0.7cm}\stmt{GREY\_TAPE isOn TABLE}\\
\hline
\end{tabular}
}\hspace{1em}%
\subfigure{
\begin{tabular}{l}
\hline
Robot's beliefs about the human (\emph{human's model})\\
\hline
  \hspace{0.7cm}\stmt{PINK\_TRASHBIN isReachable false}\\
  \hspace{0.7cm}\stmt{WALLE\_TAPE isReachable {\bf true}}\\
      \hspace{0.7cm}\stmt{LOTR\_TAPE isReachable {\bf false}}\\
      \hspace{0.7cm}\stmt{GREY\_TAPE isReachable {\bf false}}\\
  \hspace{0.7cm}\stmt{WALLE\_TAPE isVisible true}\\
  \hspace{0.7cm}\stmt{LOTR\_TAPE isVisible true}\\
  \hspace{0.7cm}\stmt{GREY\_TAPE isVisible true}\\
  \hspace{0.7cm}\stmt{WALLE\_TAPE isOn TABLE}\\
  \hspace{0.7cm}\stmt{LOTR\_TAPE isOn TABLE}\\
  \hspace{0.7cm}\stmt{GREY\_TAPE isOn TABLE}\\ 
 \hline
\end{tabular}
}
\end{center}
\caption{Symbolic facts computed from the situation depicted in
Figure~\ref{fig:sparkSubfigures}. Note how reachability differs for the two
agents.}

@@

\subsubsection{Situation Assessment}

\paragraph{Symbolic Facts Production}

\begin{inparaenum}[\itshape 1\upshape)]
Geometric state of the world is abstracted in symbolic facts that can be
classified in three different categories: \item relative positions of object and
agents, \eg  \stmt{GREY\_TAPE isOn TABLE}, \item perception and manipulation
capacity and state of agents, \eg \stmt{ROBOT looksAt GREY\_TAPE},
\stmt{GREY\_TAPE isVisibleBy HUMAN1}, \item motion status for object or
agent parts, \eg \stmt{GREY\_TAPE isMoving true}, \stmt{ROBOT\_HEAD
isTurning true}.
\end{inparaenum}
By reasoning about human perspective, it computes facts such as:
\stmt{GREY\_TAPE isBehind HUMAN1}, \stmt{GREY\_TAPE leftOf HUMAN1}.

As an illustration, Figure~\ref{fig::reach-ex} explains how the \emph{reachable}
affordance is mutually computed for the human and the robot. The \emph{is visible},
\emph{looks at}, \emph{points at} affordances are computed in similar ways, by
virtually placing OpenGL cameras in different pose (human head pose, robot head
pose, human index finger, etc.) and evaluating which objects are visible to the camera
(hence taking into account possible occlusions).

\begin{figure*}[!t]
	\centering
    \subfigure[] { \includegraphics[width=0.2\textwidth]{reachex-1.png} }
    \subfigure[] {\includegraphics[width=0.2\textwidth]{reachex-2.jpg} }
    \subfigure[] {\includegraphics[width=0.2\textwidth]{reachex-3.jpg} }
    \subfigure[] {\includegraphics[width=0.2\textwidth]{reachex-4.jpg} }
    \caption{An example illustrating the \textit{reachable} relation. The
        relation is computed from the perspectives of both the robot and the
        human. The computed posture at each step is illustrated with a global
        view of the scene (top), and from a closest view (bottom). The robot
        and its human partner are placed face to face (a).  The robot first
        estimates if the small grey box is reachable to itself using an inverse
        kinematic (IK) solver and collision checks to find a collision free
        posture to reach the object (b). Next the robot switches to the human's
        perspective to estimate if the same object is reachable to the human as
        well (c).  In the last scene, the human moves towards his left, farther
        from the object (d). The situation is then reevaluated. In this occasion
        though, the reasoner cannot find a satisfactory posture for the human to
    reach the box because he is too far from the target.  }

\label{fig::reach-ex}
\end{figure*}

@@

It is sometimes difficult or even impossible to see and/or track an object in
certain states. This happens, for instance, when the object is hidden in a
container, when the robot holds it in its gripper, and more generally in any
state in which it is hidden by something else. {\sc Spark} models the possible
symbolic states of objects (whether the object is on a furniture, in an agent
hand, in a container, etc.): According to the robot perception of what has
happened since the object was last seen, the robot builds a belief of the
current possible state with associated probability model.

\paragraph{Primitive Action Recognition}

@@

\subsubsection{Ego-centric and Allo-centric Frames}

{\sc Spark} also supports \emph{perspective-taking}: spatial relations between entities can
be computed from different viewpoints, which let the robot build for each
agents it interacts with a different, \emph{perspective-aware} symbolic model
of the environment. These models are separately stored in the knowledge base.

This allows us to deal with ambiguities that arise when one speaker refers to
an object within a reference system (or changes the reference system, \ie
switches perspective) without making the reference frame
explicit~\cite{Breazeal2006, Ros2010}.

As a result, the robot stores models of the environment either in the
\emph{ego-centric} reference frame (from the robot perspective) or in 
\emph{allo-centric} frames (addressee-centred).

\subsubsection{Specific Limitations}

One of the main limit of our current approach is the way semantics are
conveyed: because we use 2D markers for artifacts, we skip most of the object
extraction and recognition challenges. Each object has a unique identifier,
which enable us to load a proper CAD model suitable for 3D spatial reasoning
and prevent recognition mistakes in the knowledge base. While {\sc Spark}
algorithms themselves are ignorant of the input sources, and would work equally
well with a full object recognition stack, we do not have tackled it yet.

>>>>

\subsection{Acquiring and Anchoring Knowledge in the Physical World}
\label{sect|sit-ass}

@@

{\sc Spark} is designed to run and continuously update the knowledge base (in our
experiments, it runs at about 10Hz). At each steps, it re-computes spatial
relationships and affordances for the whole scene, and send the delta (new
relations and relations that do not hold anymore) to the knowledge base. This
approach may raise scalability concerns (we did not however hit such issues in
our constrained scenarios), but greatly simplifies the management of the
\emph{dynamics} of the knowledge (\emph{When do I discard outdated knowledge?
When do I update it?}). Since it is equivalent to a reset of the reasoner
domain, it also hides issues linked to non-monotonic reasoning
(see~\cite{McCarthy2007} for a discussion on that question).

\begin{figure*}[ht!]
   \begin{center}
%
       \subfigure[Physical setting]{%
%           \label{fig:wuweiPhoto}
           \includegraphics[width=0.5\textwidth]{etat2-P1010769_brightened-v2.jpg}
       }%
       \subfigure[Corresponding 3D model view]{%
%          \label{fig:sparkScreenshot}
          \includegraphics[width=0.43\textwidth]{etat2_photo.png}
       }\\ %  ------- End of the first row ----------------------%
%
   \end{center}

   \caption{Toy scenario involving videotapes that have to be manipulated, with
       other objects used as supports and containers.  After identification and
       localisation of the set of objects and acquisition of the position and
       posture of the human partner, the robot is able to compute that two tapes
       only are reachable by itself: the black and grey (in the 3D model) tapes.
       The third tape and the pink box are only reachable by the human. This
       situation leads to the symbolic model presented in
       Table~\ref{table|beliefsfig7}.  }%

@@

\begin{table}
\begin{center}
    \subfigure{
\begin{tabular}{l}
\hline
Robot's beliefs about itself (\emph{robot's model})\\
\hline
  \hspace{0.7cm}\stmt{PINK\_BOX isReachable false}\\
  \hspace{0.7cm}\stmt{WHITE\_TAPE isReachable {\bf false}}\\
  \hspace{0.7cm}\stmt{BLACK\_TAPE isReachable {\bf true}}\\
  \hspace{0.7cm}\stmt{GREY\_TAPE isReachable {\bf true}}\\
  \hspace{0.7cm}\stmt{WHITE\_TAPE isVisible true}\\
  \hspace{0.7cm}\stmt{BLACK\_TAPE isVisible true}\\
  \hspace{0.7cm}\stmt{GREY\_TAPE isVisible true}\\
  \hspace{0.7cm}\stmt{WHITE\_TAPE isOn TABLE}\\
  \hspace{0.7cm}\stmt{BLACK\_TAPE isOn TABLE}\\
  \hspace{0.7cm}\stmt{GREY\_TAPE isOn TABLE}\\
\hline
\end{tabular}
}\hspace{1em}%
\subfigure{
\begin{tabular}{l}
\hline
Robot's beliefs about the human (\emph{human's model})\\
\hline
  \hspace{0.7cm}\stmt{PINK\_BOX isReachable false}\\
  \hspace{0.7cm}\stmt{WHITE\_TAPE isReachable {\bf true}}\\
      \hspace{0.7cm}\stmt{BLACK\_TAPE isReachable {\bf false}}\\
      \hspace{0.7cm}\stmt{GREY\_TAPE isReachable {\bf false}}\\
  \hspace{0.7cm}\stmt{WHITE\_TAPE isVisible true}\\
  \hspace{0.7cm}\stmt{BLACK\_TAPE isVisible true}\\
  \hspace{0.7cm}\stmt{GREY\_TAPE isVisible true}\\
  \hspace{0.7cm}\stmt{WHITE\_TAPE isOn TABLE}\\
  \hspace{0.7cm}\stmt{BLACK\_TAPE isOn TABLE}\\
  \hspace{0.7cm}\stmt{GREY\_TAPE isOn TABLE}\\ 
 \hline
\end{tabular}
}
\end{center}
\caption{Symbolic facts computed from the situation depicted in
Figure~\ref{fig:sparkSubfigures}. Note how reachability differs for the two
agents.}

@@

\subsubsection{Building an Agent-aware Symbolic Model of the Environment}
\label{sect|situ}

\paragraph{On Perspective Taking} Visual perspective taking refers to the
ability for visually perceiving the environment from other's point of view.
This ability allows us to identify the objects in situations where the visual
perception of one person differs from the other one. In developmental
psychology, one typical example consists of two similar objects in a room (\eg.
two balls) where both are visible for the child, but only one is visible for
the adult. Thus, when the adult asks the child to hand over ``the ball'', the
child is able to correctly identify which ball the adult is referring to (\ie
the one visible from the adult point of view), without asking~\cite{Moll2006}.

Besides, in order to compute a visual perspective, the actual visibility alone
is not enough. We include not only what the other person sees in a given
moment, but also what he \emph{can} see with a minimal effort (moving the eyes
or the head). To model the potential visibility of an object we compute a
visibility ratio while turning the head of the agent model towards the object.

Spatial perspective taking refers to the qualitative spatial location of
objects (or agents) with respect to a frame (\eg \emph{the keys on my left}).
Based on this frame of reference, the description of an object
varies~\cite{Marin2008}. Humans mix perspectives frequently during interaction.
This is more effective than maintaining a consistent one, either because the
(cognitive) cost of switching is lower than remaining with the same
perspective, or if the cost is about the same, because the spatial situation
may be more easily described from one perspective rather than
another~\cite{Tversky1999}. Ambiguities arise when one speaker refers to an
object within a reference system (or changes the reference system, \ie switches
perspective) without informing his/her partner about it~\cite{Breazeal2006,
Ros2010}. For example, the speaker could ask for the ``keys on the left''.
Since no reference system has been given, the listener would not know where
exactly to look.  However, asking for ``the keys on your left'' gives enough
information to the listener to understand where the speaker is referring to. On
the contrary, when using an exact, unambiguous term of reference to describe a
location (\eg. ``go north'') no ambiguity arises.

In {\sc Spark}, we use two types of the frames of reference: \emph{egocentric}
(from the robot perspective) and \emph{allo-centric}, \ie addressee-centred
(from the human perspective).

\paragraph{Symbolic Locations}

Humans commonly refer to the positions of objects with symbolic descriptors
(like \emph{on}, \emph{next to}...) instead of precise, absolute positions.
These type of descriptors have been studied in the context of language
grounding \cite{O'Keefe1999,Matuszek2010,Regier2001,Kelleher2006,Blisard2005}.
In {\sc Spark} we focus on agent-independent symbolic locations and agent-dependent,
relative locations.

\paragraph{Agent-Independent Locations}

We can refer to object locations with respect to other objects in the
environment, such as \emph{above, next to, in}, etc. {\sc Spark} computes
three main relations based on the bounding box and centre of mass of the
objects (Figure~\ref{fig|spark-oro}\emph{a}):

\begin{itemize}
	\item \concept{isOn}: computes if an object $O_1$ is on another object $O_2$ by
	evaluating the center of mass of $O_1$ according to the bounding box of $O_2$.

	\item \concept{isIn}: evaluates if an object $O_1$ is inside another object
	$O_2$ based on their bounding boxes $BB_{O_1}$ and $BB_{O_2}$.

	\item \concept{isNextTo}: indicates whether an object $O_1$ is next to another
	object $O_2$. We cannot use a simple distance threshold to determine if two
	objects are next to each other since the relation is highly dependent on the
	dimensions of the objects. For instance, the maximum distance between large
	objects (\eg two houses) to consider them as being next to each other is much
	larger than the maximum distance we would consider for two small objects (\eg
	two bottles). Thus, the relation between the dimensions and the distances of
	the objects are taken into account.

\end{itemize}

{\sc Spark} also compute symbolic facts related to agent independent world dynamics.
The predicate \concept{isMoving} states, for each tracked entity, whether it is
currently moving or not.

\paragraph{Agent-Dependent Placements}

While in previous section we listed several \emph{absolute} location predicate,
many topological relations are directly dependent from the observation point.

The predicate \concept{hasRelativePosition} represents spatial locations
between agents and objects that are agent dependent.  We compute these spatial
locations by dividing the space around the referent (an agent) into $n$ regions
based on arbitrary angle values relative to the referent orientation
(Figure~\ref{fig|spark-oro}\emph{b}).  For
example, for $n = 4$ we would have the space divided into \emph{front, left,
right} and \emph{back}. Additionally, two proximity values, \emph{near} and
\emph{far}, are also considered. The number of regions and proximity values can
be chosen depending on the context where the interaction takes place.

Through perspective taking, {\sc Spark} computes for each agent a symbolic
description of the relative positioning of objects in the environment.

\subsubsection{Building a Model of Agents}
\label{sect|grounding_agents}

Building a grounded symbolic model of the physical environment does not suffice
in general to fully ground the human-robot interaction, and a model of the
current capabilities of the agents surrounding the robot is also required.

There are a number of common properties for a robot and a human related to
their capabilities in a given situation: they can both reach, grasp, look at,
point at, etc.: we group them in the \emph{Agent} category, defined as entities
that can act in the environment and manipulate it.

{\sc Spark} computes the following capabilities from the perspectives of each agent:

\begin{itemize}

\item \emph{Sees}: An important ability to know about an agent is to predict
\emph{What can it see?}, \ie what is within its field of view (FOV). Being able
to compute this information, the robot can reuse it for instance to infers
which object a human is searching for (the one that is not currently visible,
otherwise the user would not be searching for it).  In
figure~\ref{fig|spark-oro}\emph{c} the field of view of a person is
illustrated with a grey cone (broader one). While he is able to see the two
small boxes on the table in front of him, the big box on his right is out of
his FOV, and therefore, he is not able to see it.

\item \emph{Looks At}: this relation corresponds to what the agent is focused
on, \ie where its focus of attention is directed. This model is based on a
narrower field of view, the field of attention (FOA). 
Figure~\ref{fig::sparkRepresentations}\emph{c}
shows the field of attention of a person with a green cone (narrower one). In
this example only the grey box satisfies the \concept{looksAt} relation.

\item \emph{Points At}: verifies whether an object is pointed at by an agent.
    This relation is computed by placing a virtual camera on the hand, aligned
    with the forearm. \concept{pointsAt} is particularly useful during
    interaction when one of the agents is referring to an object saying ``this''
    or ``that'' while pointing at it.

If a larger object occludes a smaller one while an agent is pointing at them, the
outcome of the evaluation will result only in one relation, \ie \stmt{agent\_01
pointsAt object\_01} since the small one is not visible to the agent.  On the
contrary, if the small object is in front of the big one, then both objects
will satisfy the relation, which may generate an ambiguity (which object the
agent refers to?) that is let to be solved by other discrimination algorithms.

To make recognition more robust, these three first capabilities are filtered
with an hysteresis function at the geometric level.

\item \emph{Reachable}: it allows the robot to estimate the agent's capability
to reach an object, which is fundamental for task planning. For example, if the
user asks the robot to give him/her an object, the robot must compute a transfer
point where the user is able to get the object afterwards. 
Figure~\ref{fig::reach-ex} explains how addressee-dependent reachability is
computed, based on Generalized Inverse Kinematics and collision detection.

\end{itemize}

Table~\ref{facts} lists all the symbolic facts that are computed by {\sc Spark},
along with the type of the statements' subjects and objects.

\renewcommand{\concept}[1]{{\scriptsize \texttt{#1}}}
\begin{table}[h]
    \centering
    \begin{tabular}{p{1.5cm}lp{2cm}p{3.7cm}}
    \textbf{Subject} & \textbf{Predicate} & \textbf{Object} & \emph{Notes} \\ 
    \hline
	 \concept{Location} & \concept{isAt} $\equiv$ \concept{cyc:objectFoundInLocation}  &  \concept{Location} & \\ 
	 &  $\rightarrow$ \concept{isOn} $\equiv$ \concept{cyc:above\_Touching}  &  & \\ 
	 &  $\rightarrow$ \concept{isIn}  &  & \\ 
	 &  $\rightarrow$ \concept{isNextTo}  & &  \\ 
	 \concept{Location}  & \concept{isAbove} $\equiv$ \concept{cyc:above-Generally}  &  \concept{Location}  &  inverse of \concept{isBelow} \par \concept{isOn} $\Rightarrow$ \concept{isAbove}\\ 
	 \concept{Location}  & \concept{isBelow}  & \concept{Location}  &  inverse
	of \concept{isAbove} \\
	\hline
	 \concept{Location}  & \concept{hasRelativePosition}  & \concept{Location} & \\ 
	 & 	$\rightarrow$ \concept{behind} $\equiv$ \concept{cyc:behind-Generally}  &  & inverse of \concept{inFrontOf}  \\ 
	 &  $\rightarrow$ \concept{inFrontOf} $\equiv$ \concept{cyc:inFrontOf-Generally}  & 	 & 	 inverse of \concept{behind}  \\ 
	 &  $\rightarrow$ \concept{leftOf}  &  &  inverse of \concept{rightOf} \\ 
	 &  $\rightarrow$ \concept{rightOf}  & 	 & 	 inverse of \concept{leftOf}  \\ 
	 \concept{Object}  & \concept{cyc:farFrom}  &  \concept{Agent} & \\ 
	 \concept{Object}  & \concept{cyc:near}  &  \concept{Agent} & \\

		\hline
		 \concept{Agent}  & \concept{looksAt}  & \concept{SpatialThing} \\
		 \concept{Agent}  & \concept{sees}  &  \concept{SpatialThing}  &    \\ 
		 \concept{SpatialThing}  & \concept{isInFieldOfView}  &  \concept{xsd:boolean}  & via inference: \par \tiny \stmt{myself sees *} $\Leftrightarrow$ \stmt{* isInFieldOfView true} \\ 
		 \concept{Agent}  & \concept{pointsAt} $\equiv$ \concept{cyc:pointingToward}  & \concept{SpatialThing} \\ 
		 \concept{Agent}  & \concept{focusesOn}  &  \concept{SpatialThing}  &  via inference: \par \tiny \concept{looksAt} $\wedge$ \concept{pointsAt} $\Rightarrow$ \concept{focusesOn} \\
		\concept{Agent} & \concept{seesWithHeadMovement} &  \concept{SpatialThing} \\
		\concept{Agent} & \concept{reaches} &  \concept{Object} \\

	\end{tabular}

    \caption{List of statements describing agent-independent spatial
        relationships between objects (top), agent-dependent placements (middle)
        and attentional states and abilities of agents (bottom).
        ``$\rightarrow$'' indicates sub-properties. When existing, the
        equivalent predicate in the {\sc OpenCyc} standard (prefix \concept{cyc:})
        is specified. Note that some relationships are not computed by {\sc Spark}, but
        are instead inferred by the reasoner.}

	\label{facts}
\end{table}
\renewcommand{\concept}[1]{{\small \texttt{#1}}}

%\subsubsection{Situation Assessment}
%
%\paragraph{Symbolic Facts Production} 
%
%\begin{inparaenum}[\itshape 1\upshape)]
%Geometric state of the world is abstracted in symbolic facts that can be
%classified in three different categories: \item relative positions of object and
%agents, \eg  \stmt{GREY\_TAPE isOn TABLE}, \item perception and manipulation
%capacity and state of agents, \eg \stmt{ROBOT looksAt GREY\_TAPE},
%\stmt{GREY\_TAPE isVisibleBy HUMAN1}, \item motion status for object or
%agent parts, \eg \stmt{GREY\_TAPE isMoving true}, \stmt{ROBOT\_HEAD
%isTurning true}.
%\end{inparaenum}
%By reasoning about human perspective, it computes facts such as:
%\stmt{GREY\_TAPE isBehind HUMAN1}, \stmt{GREY\_TAPE leftOf HUMAN1}.
%
%As an illustration, Figure~\ref{fig::reach-ex} explains how the \emph{reachable}
%affordance is mutually computed for the human and the robot. The \emph{is visible},
%\emph{looks at}, \emph{points at} affordances are computed in similar ways, by
%virtually placing OpenGL cameras in different pose (human head pose, robot head
%pose, human index finger, etc.) and evaluating which objects are visible to the camera
%(hence taking into account possible occlusions).
%
%\begin{figure*}[!t]
%	\centering
%    \subfigure[] { \includegraphics[width=0.2\textwidth]{reachex-1.png} }
%    \subfigure[] {\includegraphics[width=0.2\textwidth]{reachex-2.jpg} }
%    \subfigure[] {\includegraphics[width=0.2\textwidth]{reachex-3.jpg} }
%    \subfigure[] {\includegraphics[width=0.2\textwidth]{reachex-4.jpg} }
%    \caption{An example illustrating the \textit{reachable} relation. The
%        relation is computed from the perspectives of both the robot and the
%        human. The computed posture at each step is illustrated with a global
%        view of the scene (top), and from a closest view (bottom). The robot
%        and its human partner are placed face to face (a).  The robot first
%        estimates if the small grey box is reachable to itself using an inverse
%        kinematic (IK) solver and collision checks to find a collision free
%        posture to reach the object (b). Next the robot switches to the human's
%        perspective to estimate if the same object is reachable to the human as
%        well (c).  In the last scene, the human moves towards his left, farther
%        from the object (d). The situation is then reevaluated. In this occasion
%        though, the reasoner cannot find a satisfactory posture for the human to
%    reach the box because he is too far from the target.  }
%
%\label{fig::reach-ex}
%\end{figure*}
%

@@

\fxfatal{Rephrase}
It is sometimes difficult or even impossible to see and/or track an object in
certain states. This happens, for instance, when the object is hidden in a
container, when the robot holds it in its gripper, and more generally in any
state in which it is hidden by something else. {\sc Spark} models the possible
symbolic states of objects (whether the object is on a furniture, in an agent
hand, in a container, etc.): According to the robot perception of what has
happened since the object was last seen, the robot builds a belief of the
current possible state with associated probability model.

\subsubsection{Primitive Action Recognition}

@@

%\subsubsection{Ego-centric and Allo-centric Frames}
%
%{\sc Spark} also supports \emph{perspective-taking}: spatial relations between entities can
%be computed from different viewpoints, which let the robot build for each
%agents it interacts with a different, \emph{perspective-aware} symbolic model
%of the environment. These models are separately stored in the knowledge base.
%
%This allows us to deal with ambiguities that arise when one speaker refers to
%an object within a reference system (or changes the reference system, \ie
%switches perspective) without making the reference frame
%explicit~\cite{Breazeal2006, Ros2010}.
%
%As a result, the robot stores models of the environment either in the
%\emph{ego-centric} reference frame (from the robot perspective) or in 
%\emph{allo-centric} frames (addressee-centred).

\subsubsection{Limitations}

The main weakness of our current implementation relates to the way semantics are
conveyed: because we use 2D markers for artifacts, we skip most of the object
extraction and recognition challenges. Each object has a unique identifier,
which enable us to load a proper CAD model suitable for 3D spatial reasoning
and prevent recognition mistakes in the knowledge base. While {\sc Spark}
algorithms themselves are ignorant of the input sources, and would work equally
well with a full object recognition stack, we do not have tackled it yet.
